Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-04 ms.tex
section 4

  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &   $r_{\rm s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.2}{\eta}\right)_{r_{s}}^{(c)}$} &

@@

We include a few solutions with cooling (marked with a $\dagger$) and
conductivity (marked with a $\ddagger$) Table \ref{table:models} to
assess whether it is valid to neglect these effects. As expected
solutions for which $\dot{q}_{\rm heat}/\dot{q}_{\rm rad}\gg 1$ are
unaffected when radiative cooling is included (see the solution with
$\Mbh=10^{8} \Msun, v_w=600 {\rm km/s and} \gamma=0.8$. However, we
find that as we decrease the heating further, to cooling begins to
become more important (see $\Mbh=10^{8} \Msun, v_w=450 {\rm km/s and}
\gamma=0.8$). Overall, we find radiative cooling has negligible effect
on cusp solutions $v_w\geq 600 km/s$ in and core solutions with
$v_w=1200$ km/s {\bf AG for the purposes of description it may be
  simpler to just rerun all of our models with radiative cooling}.

We re-ran all cusps ($\Gamma=0.8$) with $v_w=300$ km/s and
all cores ($\Gamma=0.1$) with $v_w=600 $ km/s with radiative cooling
for three different values of the mass input parameter $\eta$--0.02,
0.2, and 0.6.  Note that $\eta=0.02$ is the minimum expected physical
mass input parameter. Solutions which were unstable for all values of
$\eta$ are marked with a $\mathbf{TI}$ {\bf solution that were
  unstable for only some choices of eta}.

@@

In addition to our standard set of solutions neglecting thermal conduction and cooling, we explore a few test simulations including these effects, as marked by dagger symbols in Table \ref{table:models}.  For solutions which are far from being thermally unstable when cooling is neglected (e.g. $M_{\bullet} = 10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta = 0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), the effects of including radiative cooling on the key properties of the flow (stagnation radius, mass accretion rate, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ ratio) are small.  However, for solutions in which cooling stability is marginal (e.g. $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \sim $few), including cooling decreases the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a greater fraction.  Likewise, we find that the key properties of solutions including thermal conduction are always minor for our choice of the saturation parameter $\phi = 0.1$, and they act to offset the effects of radiative cooling, i.e. to make the flow more thermally stable (e.g.~\citealt{Zakamska&Narayan03}).

>>>>

  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &   $r_{\rm s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{\eta}{0.2}\right)_{r_{s}}^{(c)}$} &

@@

@@

In addition to our standard set of solutions neglecting thermal conduction and cooling, we explore a few test simulations including these effects, as marked by dagger symbols in Table \ref{table:models}.  For solutions which are far from being thermally unstable when cooling is neglected (e.g. $M_{\bullet} = 10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta = 0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), the effects of including radiative cooling on the key properties of the flow (stagnation radius, mass accretion rate, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ ratio) are small.  However, for solutions in which cooling stability is marginal (e.g. $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \sim $few), including cooling decreases the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a greater fraction.  In particular, we ran solutions with radiative cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and all cores with $v_w=600 $ km s$^{-1}$, each for three different values of the mass input parameter spanning the physically expected range $\eta = 0.02,
0.2, 0.6$.  Solutions which are found to be unstable for all values of $\eta$ are marked with a $\mathbf{TI}$ in Table \ref{table:models}.

Likewise, we find that the key properties of solutions including thermal conduction are always minor for our choice of the saturation parameter $\phi = 0.1$, and they act to offset the effects of radiative cooling, i.e. to make the flow more thermally stable (e.g.~\citealt{Zakamska&Narayan03}).
